---
title: "Tutorial for R for Data Science Ch 3 & 5"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
tutorial_options(exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(nycflights13)
```


## Section 3.3.1 

### 3.3.1 Easy DN

#### Exercise 1 DN

Write the R code for putting mpg dataset into a mpg dataframe

```{r D1, exercise=TRUE}

```

```{r D1-solution, include=FALSE}
mpg<- data.frame(mpg)
```

```{r D1-check}
gradethis::grade_this_code()
```

#### Exercise 2 DN

Write the R code for Viewing the mpg dataframe
```{r D2, exercise=TRUE}

```

```{r D2-solution}
View(mpg)
```

```{r D2-check}
gradethis::grade_this_code()
```

###  3.3.1 Intermediate DN

#### Exercise 12 DN
Refer to mpg data set.  

Plot a geom_point graph with displ on x-axis, hwy on y-axis, and map the shape of points to drv
```{r D12, exercise=TRUE}
ggplot(    ) + 
  geom_point(    )
```

```{r D12-hint}
"Mapping the shape of points to drv means that the argument should be included inside aesthetic"
```

```{r D12-solution}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape= drv))
```

```{r D12-check}
gradethis::grade_this_code()
```


#### Exercise 13 DN

```{r D13}
quiz(
  question("Which of the following are considered asethetics in geom_point ?",
    answer("fill", correct = TRUE),
    answer("shape", correct = TRUE),
    answer("size", correct= TRUE),
    answer("length")
  )
)
```
### 3.3.1 Advanced DN  

#### Exercise 23 DN

Divide mpg dataframe into 2 half and plot 2 separate geom_point graphs respectively with displ on x-axis and hwy on y-axis  
**HINT**:"spliting the mpg dataframe requires floor(), set.seed(), sample(), seq_len()"

```{r D23, exercise=TRUE}
half_size <- floor(0.5*  )
set.seed(123123)
mpg_half <- sample(seq_len(   ), size= half_size)

mpg_1 <- mpg[mpg_half, ]
mpg_2 <- mpg[-mpg_half, ]

ggplot(data= mpg_1) +
  geom_point(  )
ggplot(data=mpg_2) +
  geom_point(  )
```

```{r D23-solution}
half_size <- floor(0.5*nrow(mpg))
set.seed(123123)
mpg_half <- sample(seq_len(nrow(mpg)),size= half_size)

mpg_1 <- mpg[mpg_half, ]
mpg_2 <- mpg[-mpg_half, ]

ggplot(data= mpg_1) +
  geom_point(mapping = aes(x= displ, y = hwy))
ggplot(data=mpg_2) +
  geom_point(mapping = aes(x= displ, y = hwy))
```

```{r D23-check}
gradethis::grade_this_code()
```

## Section 3.6.1 DN

### 3.6.1 Easy DN

#### Exercise 3 DN

```{r D3}
quiz(
  question("Which of the following are considered variables in facet_wrap ?",
    answer("rows"),
    answer("cols"),
    answer("nrow", correct= TRUE),
    answer("ncol", correct= TRUE)
  )
)
```

#### Exercise 4 DN

```{r D4}
quiz(
  question("Which of the following are considered variables in facet_grid ?",
    answer("rows", correct= TRUE),
    answer("cols", correct= TRUE),
    answer("nrow"),
    answer("ncol")
  )
)
```

### 3.6.1 Intermediate DN

#### Exercise 14 DN

Recreate the R code necessary to generate the following graphs
```{r D14-graph}
ggplot(data=mpg, mapping = aes(x= displ, y= hwy)) +
  geom_point() +
  geom_line()
```

```{r D14, exercise=TRUE}
ggplot(data=mpg, mapping = aes(   ,   )) +
  geom_point() +
  geom_line()
```

```{r D14-hint}
"You would need 2 geom graphs"
```

```{r D14-solution}
ggplot(data=mpg, mapping = aes(x= displ, y= hwy)) +
  geom_point() +
  geom_line()
```

```{r D14-check}
gradethis::grade_this_code()
```

#### Exercise 15 DN

Recreate the R code necessary to generate the following graphs
```{r D15-graph}
ggplot() +
  geom_point(data=mpg, mapping= aes(x=displ, y= hwy, color= drv)) +
  geom_line(data=mpg, mapping = aes(x=displ, y= hwy, color= drv))

```

```{r D15, exercise=TRUE}
ggplot() +
  geom_point() +
  geom_line()

```

```{r D15-hint}
"You should map the color of points to drv variable"
```

```{r D15-solution}
ggplot() +
  geom_point(data=mpg, mapping= aes(x=displ, y= hwy, color= drv)) +
  geom_line(data=mpg, mapping = aes(x=displ, y= hwy, color= drv))
```

```{r D15-check}
gradethis::grade_this_code()
```  

### Advanced 3.6.1 DN

#### Exercise 24 DN

Refer to the mpg dataset.  

Write the R code to plot 1 geom_point graph and 1 geom_smooth graph, with color=class, excluding all 2seater cars  

```{r D24, exercise=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
   geom_point(data =   ) + 
   geom_smooth(data = , se=FALSE)
```

```{r D24-hint}
"Remind yourself how you utilized filter() function earlier "
```

```{r D24-solution}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
   geom_point(data = filter(mpg, class != "2seater"), mapping = aes(color = class)) + 
   geom_smooth(data = filter(mpg, class != "2seater"), se= FALSE)
```

```{r D24-check}
gradethis::grade_this_code()
```

## Section 5.2.4 DN

### Easy 5.2.4 DN

#### Exercise 5 DN

Refer to flights dataset.
Find all flights that arrived on Christmas Eve (24th December)

```{r D5, exercise=TRUE}
filter(flights,     &     )
```

```{r D5-hint}
"Experiment with the filter() function"
```

```{r D5-solution}
filter(flights, month == 12 & day == 24)
```

```{r D5-check}
gradethis::grade_this_code()
```

### Intermediate 5.2.4 DN  

#### Exercise 16 DN  

Refer to flights dataset.
Find all flights with missing dep_delay, and arr_delay  

```{r D16, exercise=TRUE}
filter(flights,     &     )
```


```{r D16-hint}
"Experiment with is.na() and filter() function"
```

```{r D16-solution}
ggplot() +
  geom_point(data=mpg, mapping= aes(x=displ, y= hwy, color= drv)) +
  geom_line(data=mpg, mapping = aes(x=displ, y= hwy, color= drv))
```

```{r D16-check}
gradethis::grade_this_code()
```

### Advanced 5.2.4 DN  

#### Exercise 25 DN  

Refer to flights dataset.
Find all flights that belong to Mesa Airlines, Hawaiian Airlines, and Alaska Airlines

```{r D25-hint}
"type airplanes in the console"
```

```{r D25, exercise=TRUE}
filter(flights, carrier ==    )
```

```{r D25-solution}
filter(flights, carrier == c("YV","HA","AS"))
```

```{r D25-check}
gradethis::grade_this_code()
```  

## Section 5.3.1 DN

### Easy 5.3.1 DN

#### Exercise 6 DN

```{r D6}
quiz(
  question("Which of the following are considered arguments in arrange() ?",
    answer("data"),
    answer(".data", correct= TRUE),
    answer("by_group"),
    answer(".by_group", correct= TRUE)
  )
)
```

#### Exercise 7 DN  

```{r D7}
quiz(
  question("Using arrange() function, where are NA values located ?",
    answer("top of the data"),
    answer("randomized"),
    answer("end of the data", correct= TRUE)
  )
)
```

### Intermediate 5.3.1 DN  

#### Exercise 17 DN 

Refer to flights dataset.
Arrange flights based on descending dep_delay  

```{r D17, exercise=TRUE}
arrange(  ,   )
```

```{r D17-hint}
"Experiment with arrange() function"
```

```{r D17-solution}
arrange(flights, desc(dep_delay))
```

```{r D17-check}
gradethis::grade_this_code()
```

#### Exercise 18 DN 

Refer to flights dataset.
Arrange flights based on ascending distance

```{r D18, exercise=TRUE}
arrange(    ,    )
```

```{r D18-hint}
"Ascending order is the default for arrange()"
```

```{r D18-solution}
arrange(flights, distance)
```

```{r D18-check}
gradethis::grade_this_code()
```

### Advanced 5.3.1 DN

#### Exercise 27 DN

Make a new column in flights dataset called speed where speed = distance/air_time. Arrange flights based on descending speed
```{r D27, exercise=TRUE}
flights <- flights %>%
  mutate(speed =   /   )
  arrange(  ,  )
```

```{r D27-hint}
"Experiment with contains() function in dplyr package "
```

```{r D27-solution}
flights <- flights %>%
  mutate(speed = distance/air_time)
  arrange(flights, desc(speed))
```

```{r D27-check}
gradethis::grade_this_code()
```

## Section 5.4.1 DN

### Easy 5.4.1 DN  

#### Exercise 8 DN  

Refer to flights dataset.
Rename air_time column to airtime 

```{r D8, exercise=TRUE}
rename(flights,   =     )
```

```{r D8-hint}
"Experiment with the rename() function"
```


```{r D8-solution}
rename(flights, airtime = air_time)
```

```{r D8-check}
gradethis::grade_this_code()
```

### Intermediate 5.4.1 DN  

#### Exercise 19 DN 

Refer to flights dataset.
Select all columns except year, month, day column  

```{r D19, exercise=TRUE}
select(flights,    )
```

```{r D19-hint}
"You can either list all other columns beside year, month, day or use `!` "
```

```{r D19-solution}
select(flights, !c(year, month, day))
```

```{r D19-check}
gradethis::grade_this_code()
```  

### Advanced 5.4.1 DN  

#### Exercise 26 DN 
Refer to flights dataset.
Select all columns not containing the word "time"

```{r D26, exercise=TRUE}
select(flights,    )
```

```{r D26-hint}
"Experiment with contains() function in dplyr package "
```

```{r D26-solution}
select(flights, !contains("time"))
```

```{r D26-check}
gradethis::grade_this_code()
```

## Section 5.5.2 DN

### Easy 5.5.2 DN

#### Exercise 9 DN

```{r D9}
quiz(
  question("Which of the following arguments control where new columns should appear in mutate() ?",
    answer(".data"),
    answer(".keep"),
    answer(".before"),
    answer(".after", correct= TRUE)
  )
)
```

#### Exercise 10 DN 

```{r D10}
quiz(
  question("Using mutate(), What will happen to NULL values in output column ?",
    answer("removed", correct= TRUE),
    answer("retained"),
    answer("changed to NA"),
    answer("changed to logical(0)")
  )
)
```

### Intermediate 5.5.2 DN

#### Exercise 20 DN  

Refer to flights dataset.
Add a new column called air_time_hours by converting air_time from minutes to hours

```{r D20, exercise=TRUE}
mutate(    ,    )
```

```{r D20-hint}
"Experiment with mutate() function "
```

```{r D20-solution}
mutate(flights, air_time_hours = air_time/60)
```

```{r D20-check}
gradethis::grade_this_code()
```

#### Exercise 21 DN  

Refer to flights dataset.
Add a new column called distance_km by converting distance from miles to km (1 mile = 1.61 km)  

```{r D21, exercise=TRUE}
mutate(    ,    )
```

```{r D21-hint}
"Experiment with mutate() function "
```

```{r D21-solution}
mutate(flights, distance_km = distance * 1.61)
```

```{r D21-check}
gradethis::grade_this_code()
```

### Advanced 5.5.2 DN  

#### Exercise 28 DN   

Refer to flights dataset.
Rank the 10 fastest flights and 10 slowest flights  

```{r D28-hint}
"Experiment with top_n() function"
```

```{r D28, exercise=TRUE}
flights <- mutate(flights, speed= distance/air_time)
arrange(  ,  ) %>% 
arrange(  ,  ) %>% 
```

```{r D28-solution}
flights <- mutate(flights, speed=distance/air_time)
arrange(flights, desc(speed)) %>% top_n(10)
arrange(flights, speed) %>% top_n(10)
```

```{r D28-check}
gradethis::grade_this_code()
```

## Section 5.6.7 DN

### Easy 5.6.7 DN  

#### Exercise 11 DN  
Refer to flights dataset.
Find the mean air time for each month

```{r D11, exercise = TRUE}
flights %>% 
  group_by( ) %>%
  summarise(mean_air_time = mean( ))
```

```{r D11-hint}
"NAs should be removed in calculating the mean air time"
```

```{r D11-solution}
flights %>% 
  group_by(year, month) %>%
  summarise(mean_air_time = mean(air_time, na.rm = TRUE))
```

```{r D11-check}
gradethis::grade_this_code()
```

### Intermediate 5.6.7 DN  

#### Exercise 22 DN  

Refer to flights dataset.
Find the median air time for each day of the year

```{r D22, exercise=TRUE}
flights %>% 
  group_by(   ) %>%
  summarise(median_air_time = median(   ))
```

```{r D22-hint}
"NAs should be removed in calculating the mean air time "
```

```{r D22-solution}
flights %>% 
  group_by(year, month, day) %>%
  summarise(median_air_time = median(air_time, na.rm = TRUE))
```

```{r D22-check}
gradethis::grade_this_code()
```

### Advanced 5.6.7 DN  

#### Exercise 29 (5.6.7)  

Refer to flights dataset.
Find the first departure and last arrival for each day of the year, and plot the following graph  

```{r D29-graph}
flights %>%
  filter(!is.na(dep_time)&!is.na(arr_time)) %>%
  group_by(year, month, day) %>%
  summarise(first_dep = first(dep_time),
            last_arr = last(arr_time)) %>%
  ggplot(aes(first_dep,last_arr)) +
  geom_smooth()
```

```{r D29, exercise=TRUE}
flights %>%
  filter(    &    ) %>%
  group_by(    ) %>%
  summarise(first_dep = first(   ),
            last_arr  =  last(   )) %>%
  ggplot(aes(first_dep,last_arr)) +
  geom_smooth()
```

```{r D29-hint}
"Refer back to our prevous exercises which use is.na(), group_by(), and summarise()"
```

```{r D29-solution}
flights %>%
  filter(!is.na(dep_time)&!is.na(arr_time)) %>%
  group_by(year, month, day) %>%
  summarise(first_dep = first(dep_time),
            last_arr = last(arr_time)) %>%
  ggplot(aes(first_dep,last_arr)) +
  geom_smooth()
```

```{r D29-check}
gradethis::grade_this_code()
```











## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
